A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-10-20 linear.tex
tiny edits

Notice also eigenfrequencies agree better for 
smaller pressure-density phase lags. While this is generally true with decreasing $\tstop$, other 
problem parameters may affect the magnitude of this phase lag, and hence the validity of the one-fluid model.  
For example, `linA' has a larger $\tstop$ than `linB', but linA's one and 
two-fluid growth rates differ by $\sim 1\%$; compare to $\sim 10\%$ error for linB. 
However, linB has a larger phase lag. This means that the effective coupling strength between dust and gas 
is problem-dependent.

>>>>

Notice also eigenfrequencies agree better for 
smaller pressure-density phase lags. While this is generally true with decreasing $\tstop$, other 
problem parameters may affect the magnitude of this phase lag, and hence the validity of the one-fluid model.  
For example, `linA' has a larger $\tstop$ than `linC', but linA's one and 
two-fluid growth rates differ by $\sim 1\%$; compare to $\sim 10\%$ error for linC. 
However, linC has a larger phase lag. This means that the effective coupling strength between dust and gas 
is problem-dependent.
